---
title: "Bivariate viz"
---
```{r}
library(tidyverse)
```

```{r}
# Load data
elections <- read.csv("https://mac-stat.github.io/data/election_2020_county.csv")
# Check it out
head(elections)
```


## Exercise 1

We need dataset, the two variables show up in the plot, and the ggplot functions. geom_point might give this plot.

## Exercise 2

```{r}
# Set up the plotting frame
# How does this differ than the frame for our histogram of repub_pct_20 alone? 
# It has two axis with numbers.
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16))

# Add a layer of points for each county
# The points show up is the frame.
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_point()

# Change the shape of the points
# The shape of the points become stars
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_point(shape = 3)

# YOU TRY: Modify the code to make the points "orange"
# NOTE: Try to anticipate if "color" or "fill" will be useful here. Then try both.
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_point(color = "orange")

# Add a layer that represents each county by the state it's in
# The points become the names of the states, it isn't very tidy.
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_text(aes(label = state_abbr))
```

## Exercise 3
### It is a strong positive relation, there are some Taxes points have higher repub_pct_20.

## Exercise 4
```{r}
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_point() +
  geom_smooth()
```


### a
```{r}
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_smooth()
```

### b
```{r}
ggplot(elections, aes(y = repub_pct_20, x = repub_pct_16)) +
  geom_point() +
  geom_smooth(method = "lm")
```


## Exercise 5

```{r}
# Scatterplot of repub_pct_20 vs median_rent
ggplot(elections, aes(y = repub_pct_20, x = median_rent)) +
  geom_point() +
  geom_smooth(method = "lm")


# Scatterplot of repub_pct_20 vs median_age
ggplot(elections, aes(y = repub_pct_20, x = median_age)) +
  geom_point() +
  geom_smooth(method = "lm")
```
These two scatterplots don't show strong relation, and the points don't display linearly. repub_pct_20 vs median_age has a weak positive association, and repub_pct_20 vs median_rent has a negative association that is stranger than repub_pct_20 vs median_age. 


## Exercise 6

```{r}
ggplot(elections, aes(y = repub_pct_20, x = historical)) +
  geom_point()
```
It is a categorical variable, the points only shows on exactly three places on x-axis.



































