---
title: "Data viz"
---


```{r}
# Import data
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```


## Exercise 1
```{r}
head(hikes)
```


## Exercise 2
```{r}

# Load the package
library(tidyverse)

```


## Exercise 3
```{r}
ggplot(hikes, aes(x = rating))
```

## Exercise 4
```{r}
# added '+ geom_bar()', bars appeared in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar()

# added 'y = "Number of hikes"', the y-axis has a name
ggplot(hikes, aes(x = rating)) +
  geom_bar() +
  labs(x = "Rating", y = "Number of hikes")

# added '+geom_bar(fill = "blue")', the bars become blue
ggplot(hikes, aes(x = rating)) +
  geom_bar(fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")

# added 'color = "orange"', and the bars have orange edges
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")

# added '+ theme_minimal()', the color of background changed
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue")  +
  labs(x = "Rating", y = "Number of hikes") +
  theme_minimal()
```

## Exercise 5
### a
#### The purpose of '+' is adding an other function to the original one.
#### Because it is a geometic graph.
#### They give names to the axis.
#### Color gives edges color, fill gives the bar color.

### b
#### We can learn that most hikes have rating moderate, and hikes with rating of difficult and easy are similar, there are slightly more easy hikes.

### c
#### The label of x axis can be "rate of hikes", and it should have a sequence of "low, moderate, difficult".

## Exercise 6

```{r}
ggplot(hikes, aes(x = elevation)) +
  geom_bar(fill = "blue")  +
  labs(x = "elevation", y = "Number of hikes") +
  theme_minimal()
```


## Exercise 7

### a
#### About 6.
#### About 2.

### b
#### The center of data is about 4300, and the data spaned from about 3700 to 5500. It is a little bit left-shifted.


## Exercise 8 & 9

```{r}
ggplot(hikes, aes(x = elevation))
```
```{r}
# added "+ geom_histogram()", bars appeared.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram()

# added 'color = "white"' for histogram, white edges between bars appeared.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white") 

# added 'fill = "blue"' for histogram, the bars became blue.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", fill = "blue") 

# added code for labels, the labels appeared.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white") +
  labs(x = "Elevation (feet)", y = "Number of hikes")

# added "binwidth = 1000" for histogram, the bars became very wide.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 1000) +
  labs(x = "Elevation (feet)", y = "Number of hikes")

# added "binwidth = 5" for histogram, the bars became very thin.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 5) +
  labs(x = "Elevation (feet)", y = "Number of hikes")

# added "binwidth = 200" for histogram, the bars became medimum.
ggplot(hikes, aes(x = elevation)) +
  geom_histogram(color = "white", binwidth = 200) +
  labs(x = "Elevation (feet)", y = "Number of hikes")
```


## Exercise 10









