---
title: "Data viz"
---


```{r}
# Import data
hikes <- read.csv("https://mac-stat.github.io/data/high_peaks.csv")
```


## Exercise 1
```{r}
head(hikes)
```


## Exercise 2
```{r}

# Load the package
library(tidyverse)

```


## Exercise 3
```{r}
ggplot(hikes, aes(x = rating))
```

## Exercise 4
```{r}
# added '+ geom_bar()', bars appeared in the plot
ggplot(hikes, aes(x = rating)) +
  geom_bar()

# added 'y = "Number of hikes"', the y-axis has a name
ggplot(hikes, aes(x = rating)) +
  geom_bar() +
  labs(x = "Rating", y = "Number of hikes")

# added '+geom_bar(fill = "blue")', the bars become blue
ggplot(hikes, aes(x = rating)) +
  geom_bar(fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")

# added 'color = "orange"', and the bars have orange edges
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue") +
  labs(x = "Rating", y = "Number of hikes")

# added '+ theme_minimal()', the color of background changed
ggplot(hikes, aes(x = rating)) +
  geom_bar(color = "orange", fill = "blue")  +
  labs(x = "Rating", y = "Number of hikes") +
  theme_minimal()
```

## Exercise 5
### a
#### The purpose of '+' is adding an other function to the original one.
#### Because it is a geometic graph.
#### They give names to the axis.
#### Color gives edges color, fill gives the bar color.

### b
#### We can learn that most hikes have rating moderate, and hikes with rating of difficult and easy are similar, there are slightly more easy hikes.

### c
#### The label of x axis can be "rate of hikes", and it should have a sequence of "low, moderate, difficult".

## Exercise 6














